Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-12-21 analysis/paper/London_HauloutBeahvior.Rmd
minor updates before Andy comments

The second set of models that included annual variation in haul-out
patterns uncovered significant contributions for linear and quadratic
interactions between day and year in both ribbon seals (day $\times$
year,
$F_{`r paste(ribbon_year_type3$day_year$Num.df, ribbon_year_type3$day_year$Den.df, sep=",")`}$
= `r ribbon_year_type3$day_year$F.value`; $p$ =
`r ribbon_year_type3$day_year$Prob.F`; day^2^:year,
$F_{`r paste(ribbon_year_type3$day2_year$Num.df, ribbon_year_type3$day2_year$Den.df, sep=",")`}$
= `r ribbon_year_type3$day2_year$F.value`; $p$ =
`r ribbon_year_type3$day2_year$Prob.F`) and spotted seals (day $\times$
year,
$F_{`r paste(spotted_year_type3$day_year$Num.df, spotted_year_type3$day_year$Den.df, sep=",")`}$
= `r spotted_year_type3$day_year$F.value`; $p$ =
`r spotted_year_type3$day_year$Prob.F`; day^2^:year,
$F_{`r paste(spotted_year_type3$day2_year$Num.df, spotted_year_type3$day2_year$Den.df, sep=",")`}$
= `r spotted_year_type3$day2_year$F.value`; $p$ =
`r spotted_year_type3$day2_year$Prob.F`). Predicted distributions of
haul-out activity were largely unimodal, but varied some among and
within years with respect to the timing and magnitude of haul-out peaks
(Figure \@ref(fig:annualHO)). It is important to note that predicted
variation in annual haul-out patterns likely reflects both process error
and sampling variability. While we did remove any years where only one
deployment in a species + age-sex group was present, there are still
some years where the pattern shown is informed by a small number of
individuals that may not represent population level processes.

@@

**Irina S. Trukhanova**: conceptualization, writing: review and editing

@@

@@

Data and code will be available as a complete research compendium on
GitHub and major versions archived at Zenodo. Original data sources for
telemetry are archived at the United States Animal Telemetry Network.

>>>>

The second set of models that included annual variation in haul-out
patterns uncovered significant contributions for linear and quadratic
interactions between day and year in both ribbon seals (day:year,
$F_{`r paste(ribbon_year_type3$day_year$Num.df, ribbon_year_type3$day_year$Den.df, sep=",")`}$
= `r ribbon_year_type3$day_year$F.value`; $p$ =
`r ribbon_year_type3$day_year$Prob.F`; day^2^:year,
$F_{`r paste(ribbon_year_type3$day2_year$Num.df, ribbon_year_type3$day2_year$Den.df, sep=",")`}$
= `r ribbon_year_type3$day2_year$F.value`; $p$ =
`r ribbon_year_type3$day2_year$Prob.F`) and spotted seals (day:year,
$F_{`r paste(spotted_year_type3$day_year$Num.df, spotted_year_type3$day_year$Den.df, sep=",")`}$
= `r spotted_year_type3$day_year$F.value`; $p$ =
`r spotted_year_type3$day_year$Prob.F`; day^2^:year,
$F_{`r paste(spotted_year_type3$day2_year$Num.df, spotted_year_type3$day2_year$Den.df, sep=",")`}$
= `r spotted_year_type3$day2_year$F.value`; $p$ =
`r spotted_year_type3$day2_year$Prob.F`). Predicted distributions of
haul-out activity were largely unimodal, but varied some among and
within years with respect to the timing and magnitude of haul-out peaks
(Figure \@ref(fig:annualHO)). It is important to note that predicted
variation in annual haul-out patterns likely reflects both process error
and sampling variability. While we did remove any years where only one
deployment in a species + age-sex group was present, there are still
some years where the pattern shown is informed by a small number of
individuals that may not represent population level processes.

@@

@@

**Justin Crawford**: investigation, methodology, validation, data curation, 
writing: review and editing

**Lori T. Quakenbush**: investigation, methodology, supervision, project
administration, writing: review and editing

**Andrew L. Von Duyke**: investigation, methodology, validation, data curation,
writing: review and editing

@@

This manuscript was developed as a reproducible research compendium. Data and
code are available on GitHub (https://github.com/jmlondon/berchukHaulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived at the United States Animal
Telemetry Network.
